The problem and promise of scale in multilayer networks

### 2020-02-02 paper/manuscript.Rmd
fix scales listed

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover classification map at varying scales relevant to caribou ecology. We aggregated the 10m landcover raster using the R package
`grainchanger` [@Graham_2019] at five scales: 100m, 250m, 500m, and 
1000m. Aggregation occurred using a modal moving window method using a circular window corresponding to the above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017).

>>>>

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover classification map at varying scales relevant to caribou ecology. We aggregated the 10m landcover raster using the R package
`grainchanger` [@Graham_2019] at five scales: 100m, 250m, 500m, and 
1000m. Aggregation occurred using a modal moving window method using a circular window corresponding to the above scales [@Graham_2019a]. 10m and 100m represents fine-scale decision making for caribou during foraging <!--(REF)-->, while re-sampling at 500m and 1000m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017).
